Follow-up Samples

### 2017-04-17 submission/supplemental.Rmd

\blandscape

@@

@@

kable(st2, format = "markdown", align = 'c', padding = 0)

**Table S3: Summary of Comparisons based on Chemotherapy or Radiation Received**

```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

chemo_rad_summary <- read.csv('../data/process/tables/probs_chemo_rad_pvalue_summary.csv', 
                              header = T, stringsAsFactors = F) %>% filter(X != "chemo_v_rads_IF") %>% 
  separate(X, c("comparison", "variable"), sep = "_") %>% 
  mutate(comparison = ifelse(comparison == "rads" | comparison == "rad", invisible("Radiation"), invisible("Chemotherapy")), 
         variable = c(rep("sobs", 2), rep("Shannon", 2), rep("Evenness", 2), rep("Thetayc", 2), rep("Positive Probability", 4)))

@@

\elandscape

@@

adn_surg_summary <- read.csv('../data/process/tables/adn_combined_probs_surgery_pvalue_summary.csv', 
                              header = T, stringsAsFactors = F) %>% 
  filter(X != "prop_surg_adn_srn") %>% 
  mutate(variable = c("sobs", "Shannon", "Evenness", "Thetayc", "Adenoma Only\nPositive Probability", "SRN Only\nPositive Probablity"))

>>>>

@@

\footnotesize

@@

kable(st2, format = "markdown", align = 'c', padding = 0)
```
\normalsize
\newpage

**Table S3: Summary of Comparisons based on Chemotherapy or Radiation Received**
\footnotesize
```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

chemo_rad_summary <- read.csv('../data/process/tables/probs_chemo_rad_pvalue_summary.csv',
                              header = T, stringsAsFactors = F) %>% filter(X != "chemo_v_rads_IF") %>%
  separate(X, c("comparison", "variable"), sep = "_") %>%
  mutate(comparison = ifelse(comparison == "rads" | comparison == "rad", invisible("Radiation"), invisible("Chemotherapy")),
         variable = c(rep("Richness", 2), rep("Shannon", 2), rep("Evenness", 2), rep("Thetayc", 2), rep("Positive Probability", 4)))

@@

```
\normalsize

@@

adn_surg_summary <- read.csv('../data/process/tables/adn_combined_probs_surgery_pvalue_summary.csv',
                              header = T, stringsAsFactors = F) %>%
  filter(X != "prop_surg_adn_srn") %>%
  mutate(variable = c("Richness", "Shannon", "Evenness", "Thetayc", "Adenoma Only\nPositive Probability", "SRN Only\nPositive Probablity"))
